A Longitudinal Analysis of the Privacy Paradox

### 2019-10-18 analyses/analyses.Rmd
- checked with newly merged data-set, exact same results

---
title: "A Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
output: 
  # pdf_document: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

```{r, echo = FALSE, include = FALSE}
# defaults
set.seed(170819)
options(digits = 3, width = 120, max.print = 100000)
knitr::opts_chunk$set(echo = T, error = F, message = F, tidy = T, warning = F, cache = T)
```

```{r Packages, include = FALSE, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

```{r include=FALSE}
# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```

>>>>

---
title: "A Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

```{r, echo=F, include=F}
# defaults
set.seed(170819)
options(digits=3, width=120, max.print=100000)
knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=F)
```

```{r Packages, include=F, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

```{r include=F}
# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```
